---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Andrew VanDyk
  - Noah Olson
  - Andrew Sarafin
  - Dominick Zittel
  - Lucas Rosa
  - Jayden Balcarczyk

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project :clap:

This is my project for Data Analytics 200. In it I will be using the tokyo-2021-datset-v3.csv to show past winners of olympic games. The data shows 86 different countries and sorts them by medals won, by Gold, Silver, Bronze and overall total.This project is important because it can be used to predict future outcomes of the olypic games. By using this data, we can see who has won the most medals and use that to determine who will win in the future.


# Variable Description

1. Rank: Where each country stands as opposed to other countries
2. Team/NOC: Each country that has participated
3. gold_medal: 1st place award for a country
4. silver_medal: 2nd place award for a country
5. bronze_medal: 3rd place award for a country
6. total: How many awards for each participant/country
7. continent: which continent each country belongs to


## Summary Statistics

```{r}
oj <- read_csv('https://avdanl.github.io/data/tokyo-2021-dataset-v3.csv')
nvars <- format(round(ncol(oj), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(oj), 0), 
                nsmall=0, 
                big.mark=",")
```

Rows: 93
Columns:9

```{r}
# 
url <- 'https://avdanl.github.io/data/tokyo-2021-dataset-v3.csv'
data <- read.csv(url)

# 
print(data)

```


## Top Ten Tokyo Olympics Teams
The Following bargraph shows the different teams in the 2021 Tokyo Olympics, and how 
many different medals they each have. The data could be used to show the odds of the next Olympic winner.


```{r}
# 
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
library(ggplot2)

#
medal_data <- data.frame(
  Rank = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
  Team = c("United States of America", "People's Republic of China", "Japan", "Great Britain", "ROC", "Australia", "Netherlands", "France", "Germany", "Italy"),
  Gold = c(39, 38, 27, 22, 20, 17, 10, 10, 10, 10),
  Silver = c(41, 32, 14, 21, 28, 7, 12, 12, 11, 10),
  Bronze = c(33, 18, 17, 22, 23, 22, 14, 11, 16, 20),
  Total_Medals = c(113, 88, 58, 65, 71, 46, 36, 33, 37, 40),
  Team_Code = c("USA", "CHN", "JPN", "GBR", "ROC", "AUS", "NED", "FRA", "GER", "ITA"),
  Region = c("North America", "Asia", "Asia", "Europe", "Europe/Asia", "Australia", "Europe", "Europe", "Europe", "Europe")
)

# 
ggplot(medal_data, aes(x = reorder(Team, Total_Medals), y = Total_Medals, fill = Region)) +
  geom_bar(stat = "identity") +
  labs(title = "Top Ten Teams in Tokyo 2021 Olympics",
       x = "Team",
       y = "Total Medals",
       fill = "Region") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



```


